---
title: A03
author: R package build
date: '2022-04-01'
slug: a03
categories: []
tags: []
---

# Library Setup

```{r}
suppressPackageStartupMessages(library("dplyr"))
suppressPackageStartupMessages(library("ggplot2"))
suppressPackageStartupMessages(library("class"))
suppressPackageStartupMessages(library("caret"))
library(gridExtra)
```

# Load the Data
```{r}
train_data = read.csv("https://raw.githubusercontent.com/JennaLeali/JennaLealisWebsite/main/train.csv")
head(train_data) 
```
```{r}
test_data = read.csv("https://raw.githubusercontent.com/JennaLeali/JennaLealisWebsite/main/test.csv")
head(test_data)
```
```{r}
survived = read.csv("https://raw.githubusercontent.com/JennaLeali/JennaLealisWebsite/main/gender_submission.csv")
head(survived)
```

# Exploratry Data Analysis 
#### How many passangers survived
```{r}
table(survived$Survived)
```
#### Survived (contains your binary predictions: 1 for survived, 0 for deceased)
#### 152 passengers survived 
#### How many men and women passengers were there? 
```{r}
table(test_data$Sex)
```
#### What is the most common ticket class
```{r}
table(test_data$Pclass)
```
#### 3rd class tickets were the most common
#### How many passengers were not related to another passenger
```{r}
table(test_data$SibSp)
```
#### 283 passengers had no relation to other passengers 
## Visualising distributions
```{r}
ggplot(data = survived) +
  geom_bar(mapping = aes(x = Survived))
```
```{r}
ggplot(data = test_data) +
  geom_histogram(mapping = aes(x = Age), binwidth = 0.9)
```
```{r}
ggplot(data = test_data, mapping = aes(x = Age, colour = Sex)) +
  geom_freqpoly(binwidth = 4)
```
```{r}
ggplot(data = test_data, mapping = aes(x = Pclass, colour = Sex)) +
  geom_freqpoly(binwidth = 0.1)
```

```{r}
data1 <- 
  survived %>% 
  group_by(Survived) 
data2 <- 
  test_data %>% 
  group_by(Age, Fare)
ggplot() +
  geom_point(data = data1, aes(x = Survived, y = Survived), color = "blue") + geom_point(data = data2, aes(x = Age, y = Fare))
```

```{r}
ggplot(data = test_data, mapping = aes(x = Fare, colour = Age)) +
  geom_freqpoly(binwidth = 4)
```

```{r}
ggplot(data = test_data, mapping = aes(x = Parch, colour = Cabin)) +
  geom_freqpoly(binwidth = .5)
```

#### Bar plots of variables
```{r}
p1 <- ggplot(test_data, aes(x=Sex)) + ggtitle("Sex") + xlab("Sex") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p2 <- ggplot(test_data, aes(x=Age)) + ggtitle("Age") + xlab("Age") + 
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p3 <- ggplot(test_data, aes(x=Pclass)) + ggtitle("Pclass") + xlab("Pclass") + 
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p4 <- ggplot(test_data, aes(x=Embarked)) + ggtitle("Embarked") + xlab("Embarked") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p5 <- ggplot(test_data, aes(x=SibSp)) + ggtitle("SibSp") + xlab("SibSp") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p6 <- ggplot(test_data, aes(x=Parch)) + ggtitle("Parch") + xlab("Parch") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
```




# Explore a pattern
```{r}
test1 <- cbind(test_data, Survived = survived$Survived)
```

```{r}
colSums(is.na(train_data))
```

```{r}
train_data_clean <- train_data %>%
    mutate(Age = if_else(is.na(Age), mean(Age, na.rm = TRUE), Age))

colSums(is.na(train_data_clean))
```

```{r}
colSums(is.na(test1))
```

```{r}
test_clean <- test1 %>% 
    na.omit()
```

```{r}
data_train <- train_data_clean %>% 
        select(-c(PassengerId, Name, Ticket, Embarked, Cabin)) %>% 
        mutate(Survived = as.factor(Survived),
           Pclass = as.factor(Pclass),
           Sex = as.factor(Sex),
           SibSp = as.factor(SibSp),
           Parch = as.factor(Parch))

data_test <- test_clean %>% 
        select(-c(PassengerId, Name, Ticket, Embarked, Cabin)) %>% 
        mutate(Survived = as.factor(Survived),
           Pclass = as.factor(Pclass),
           Sex = as.factor(Sex),
           SibSp = as.factor(SibSp),
           Parch = as.factor(Parch))
```

```{r}
str(data_train)
```

```{r}
prop.table(table(data_train$Survived))
```

# Use Logistic Regression Model
```{r}
m1 <- glm(Survived~., data_train, family = "binomial") 
summary(m1)
```

```{r}
m2 <- step(object = glm(Survived~., data_train, family = "binomial"),
                    direction = "backward")
```

```{r}
summary(m2)
```

```{r}
data_test$prob <- predict(m2, type = "response", newdata = data_test)
```

#### Distribution of predicted data

```{r}
ggplot(data_test, aes(x=prob)) +
  geom_density(lwd=0.5) +
  labs(title = "Distribution of Probability") +
  theme_minimal()
```

###### If the probability is greater than 0.5, the label will get 1 (survived). If the probability is lower than 0.5, the label will get 0 (not survived).

```{r}
data_test$pred_label <- factor(ifelse(data_test$prob > 0.5, 1, 0)) #1 = survived, 0 = not survived
data_test %>% 
    select(Survived, pred_label) %>% 
    head()
```

## Model Evaluation 
```{r}
confusionMatrix(reference = as.factor(data_test$Survived), 
                data = as.factor(data_test$pred_label), positive = "1" )
```




