---
title: CO2 Data IO
author: R package build
date: '2022-02-21'
slug: inclass2-21
categories: []
tags: []
---

# Data Types
## Cat Lovers
```{r}
library(tidyverse)
cat_lovers <- "https://raw.githubusercontent.com/dearbharat/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(cat_lovers)
```
### Sumarise Cat Lovers Data Set 
```{r}
glimpse(cat_lovers)
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```
## Fixing the bad data in the numeric colum 
```{r}
cat_lovers %>%
  mutate(number_of_cats = case_when(
    name == "Ginger Clark" ~ 2,
    name == "Doug Bass"    ~ 3,
    TRUE                   ~ as.numeric(number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Always you need to respect data types
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Now that we know what we are doing 
```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```
### Moral of the story
If your data does not behave how you expect it to, type coercion upon reading in the data might be the reason.
Go in and investigate your data, apply the fix, save your data, live happily ever after.


## Data Types In R - Coercion
```{r}
typeof(TRUE)
typeof("hello")
typeof(1.335)
typeof(7)
typeof(7L)
typeof(1:3)
```
## Concentration 
```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))
```
## Converting Between Types
```{r}
x <- 1:3
x
typeof(x)

y <- as.character(x)
y
typeof(y)

x <- c(TRUE, FALSE)
x
typeof(x)

y <- as.numeric(x)
y
typeof(y)

c(1, "Hello")
c(FALSE, 3L)
c(1.2, 3L)
c(2L, "two")
```


## Special values
```{r}
pi / 0
1/0 - 1/0
0 / 0
1/0 + 1/0
```

### NAs are special
```{r}
x <- c(1, 2, 3, 4, NA)
mean(x)
mean(x, na.rm = TRUE)
summary(x)
```
### NAs are logical
```{r}
typeof(NA)
```
## Mental model for NAs
Unlike NaN, NAs are genuinely unknown values
```{r}
TRUE | NA
FALSE | NA
```

# Data Classes
## Factors
```{r}
x <- factor(c("BS", "MS", "PhD", "MS"))
x
typeof(x)
class(x)
glimpse(x)
as.integer(x)
```
## Dates
```{r}
y <- as.Date("2020-01-01")
y
typeof(y)
class(y)
as.integer(y)
as.integer(y) / 365 # roughly 50 yrs
```
## Data Frames
```{r}
df <- data.frame(x = 1:2, y = 3:4)
df
typeof(df)
class(df)
```
## Lists
```{r}
l <- list(
  x = 1:4,
  y = c("hi", "hello", "jello"),
  z = c(TRUE, FALSE)
)
l
```
### Library 
```{r}
library(dplyr)
library(ggplot2)
```

## Lists and Data Frames
```{r}
df
df %>%
  pull(y)
```
## Read data in as character strings
```{r}
glimpse(cat_lovers)
```
### Coerce when plotting
```{r}
ggplot(cat_lovers, mapping = aes(x = handedness)) +
  geom_bar()
```
### Use forcats to manipulate factors
```{r}
cat_lovers %>%
  mutate(handedness = fct_infreq(handedness)) %>%
  ggplot(mapping = aes(x = handedness)) +
  geom_bar()
```

## Step 1. Construct dates 
```{r}
library(glue)
hotels %>%
  mutate(
    arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")
    ) %>% 
  relocate(arrival_date)
```
## Step 2. Count bookings per date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date)
```
## Step 3. Visualise bookings per date
```{r}
hotels %>%
  mutate(arrival_date = glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}")) %>%
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
### Step 1. REVISED Construct dates "as dates"
```{r}
library(lubridate)
hotels %>%
  mutate(
    arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))
    ) %>% 
  relocate(arrival_date)
```
### Step 2. Count bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date)
```
### Step 3a. Visualise bookings per date
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```
### Step 3b. Visualise using a smooth curve
```{r}
hotels %>%
  mutate(arrival_date = ymd(glue("{arrival_date_year} {arrival_date_month} {arrival_date_day_of_month}"))) %>% 
  count(arrival_date) %>%
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_smooth()
```

### Install Library 
```{r}
library(readr)
```

## Reading data
```{r}
nobel <- read_csv(file = "https://raw.githubusercontent.com/dearbharat/tidyverse/main/nobel.csv")
nobel
```

# Recording Data
