---
title: InClass2/21
author: R package build
date: '2022-02-21'
slug: inclass2-21
categories: []
tags: []
---
## Cat Lovers
```{r}
library(tidyverse)
cat_lovers <- "https://raw.githubusercontent.com/dearbharat/tidyverse/main/cat-lovers.csv"
cat_lovers <- read_csv(cat_lovers)
```
### Sumarise Cat Lovers Data Set 
```{r}
glimpse(cat_lovers)
cat_lovers %>%
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```
## Fixing the bad data in the numeric colum 
```{r}
cat_lovers %>%
  mutate(number_of_cats = case_when(
    name == "Ginger Clark" ~ 2,
    name == "Doug Bass"    ~ 3,
    TRUE                   ~ as.numeric(number_of_cats)
    )) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Always you need to respect data types
```{r}
cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    ) %>%
  summarise(mean_cats = mean(number_of_cats))
```
## Now that we know what we are doing 
```{r}
cat_lovers <- cat_lovers %>%
  mutate(
    number_of_cats = case_when(
      name == "Ginger Clark" ~ "2",
      name == "Doug Bass"    ~ "3",
      TRUE                   ~ number_of_cats
      ),
    number_of_cats = as.numeric(number_of_cats)
    )
```
### Moral of the story
If your data does not behave how you expect it to, type coercion upon reading in the data might be the reason.
Go in and investigate your data, apply the fix, save your data, live happily ever after.


## Data Types In R - Coercion
```{r}
typeof(TRUE)
typeof("hello")
typeof(1.335)
typeof(7)
typeof(7L)
typeof(1:3)
```
## Concentration 
```{r}
c(1, 2, 3)
c("Hello", "World!")
c(c("hi", "hello"), c("bye", "jello"))
```
## Converting Between Types
```{r}
x <- 1:3
x
typeof(x)

y <- as.character(x)
y
typeof(y)

x <- c(TRUE, FALSE)
x
typeof(x)

y <- as.numeric(x)
y
typeof(y)

c(1, "Hello")
c(FALSE, 3L)
c(1.2, 3L)
c(2L, "two")
```





