---
title: 'P01: Group Project '
author: R package build
date: '2022-04-05'
slug: p01-group-project
categories: []
tags: []
---

<p style="color:green">Jenna Leali, Ariely Burgos, Rachel Kavalakatt, Wesnahika Charles!</p>


## Load Library 
```{r}
suppressPackageStartupMessages(library(plyr))
suppressPackageStartupMessages(library(corrplot))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(gridExtra))
suppressPackageStartupMessages(library(ggthemes))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(MASS))
suppressPackageStartupMessages(library(randomForest))
suppressPackageStartupMessages(library(party))
suppressPackageStartupMessages(library(rmdformats))
suppressPackageStartupMessages(library(dplyr))
```

## Import Data
```{r}
bank.churn <- read.csv("https://raw.githubusercontent.com/JennaLeali/JennaLealisWebsite/main/Bank_Churn.csv")
```

## Summary of Data
```{r}
summary(bank.churn)
```

```{r}
head(bank.churn)
```
```{r}
glimpse(bank.churn)
```

## Explanation of Content
+ CustomerId: - contains random values and has no effect on customer leaving the bank
+ CreditScore: a customer with a higher credit score is less likely to leave the bank
+ Geography: customer’s location can affect their decision to leave the bank
+ Gender: explore whether gender plays a role in a customer leaving the bank
+ Age: older customers are less likely to leave their bank than younger ones
+ Tenure: number of years that the customer has been a client of the bank
+ Balance: good indicator of customer churn, as people with a higher balance in their accounts are less likely to leave the bank
+ NumOfProducts: number of products that a customer has purchased through the bank
+ HasCrCard: people with a credit card are less likely to leave the bank
+ IsActiveMember: active customers are less likely to leave the bank
+ EstimatedSalary:  people with lower salaries are more likely to leave the bank 
+ Exited: Has customer closed the bank account or a loyal customer 


<p style="color:lightblue">Churn Prediction: predicting which clients are most likely to cancel a subscription or leave a company based on their usage of the service!</p>

<p style="color:orange">Independent variables contain information about customers. Dependent variable refers to customer abandonment. Data consists of 10000 observations and 12 variables!</p>

## Remove Rows with Missing Values 
```{r}
sapply(bank.churn, function(x) sum(is.na(x)))
```

```{r}
bank.churn <- bank.churn[complete.cases(bank.churn), ]
```

## Data Wrangling 
#### Change the values in columns “HasCrCard”, "IsActiveMember", and "Exited" from 0 or 1 to “No” or “Yes”
```{r}
bank.churn$HasCrCard <- as.factor(mapvalues(bank.churn$HasCrCard,
                                      from=c("0","1"),
                                      to=c("No", "Yes")))
```

```{r}
bank.churn$IsActiveMember <- as.factor(mapvalues(bank.churn$IsActiveMember,
                                      from=c("0","1"),
                                      to=c("No", "Yes")))
```

```{r}
bank.churn$Exited <- as.factor(mapvalues(bank.churn$Exited,
                                      from=c("0","1"),
                                      to=c("No", "Yes")))
```

#### Group Tenure by Years
```{r}
min(bank.churn$Tenure); max(bank.churn$Tenure)
```

```{r}
group_tenure <- function(Tenure){
    if (Tenure >= 0 & Tenure <= 2){
        return('0-2 Years')
    }else if(Tenure > 2 & Tenure <= 4){
        return('2-4 Years')
    }else if (Tenure > 4 & Tenure <= 6){
        return('4-6 Years')
    }else if (Tenure > 6 & Tenure <=8){
        return('6-8 Years')
    }else if (Tenure > 8){
        return('> 8 Years')
    }
}

bank.churn$tenure_group <- sapply(bank.churn$Tenure,group_tenure)
bank.churn$tenure_group <- as.factor(bank.churn$tenure_group)
```


#### Remove columns not needed for analysis

```{r}
bank.churn$customerID <- NULL
```



## Exploratory Data Analysis 
#### How many customers churned?
```{r}
table(bank.churn$Exited)
```
#### 2037 customers have churned
### What is the most common geographical location?
```{r}
table(bank.churn$Geography)
```
#### France is the most common geographical location
#### What is the mean age amongst female customers?
```{r}
tapply(bank.churn$Age, bank.churn$Gender =="Female", mean)
```
#### 39 is the mean age amoungst female customers 
#### What is the mean age amongst male customers?
```{r}
tapply(bank.churn$Age, bank.churn$Gender =="Male", mean)
```
#### 38 is the mean age amoungst male customers 

#### Visualising distributions 
```{r}
ggplot(data = bank.churn) +
  geom_bar(mapping = aes(x = Exited))
```
```{r}
bank.churn %>% 
  count(Exited)
```
#### Continuous Variable (Estimated Salary) Histogram
```{r}
ggplot(data = bank.churn) +
  geom_histogram(mapping = aes(x = EstimatedSalary), binwidth = 0.9)
```

#### Explore a variety of binwidths to reveal different patterns 
```{r}
smaller <- bank.churn %>% 
  filter(EstimatedSalary < 50000)
  
ggplot(data = smaller, mapping = aes(x = EstimatedSalary)) +
  geom_histogram(binwidth = 0.1)
```

```{r}
ggplot(data = smaller, mapping = aes(x = CreditScore, colour = Exited)) +
  geom_freqpoly(binwidth = 4)
```
```{r}
ggplot(data = smaller, mapping = aes(x = EstimatedSalary, colour = Exited)) +
  geom_freqpoly(binwidth = 4)
```
```{r}
ggplot(data = smaller, mapping = aes(x = Balance, colour = Exited)) +
  geom_freqpoly(binwidth = .5)
```
```{r}
ggplot(data = bank.churn, mapping = aes(x = EstimatedSalary)) + 
  geom_histogram(binwidth = 3)
```

#### Bar plots of categorical variables 

```{r}
p1 <- ggplot(bank.churn, aes(x=Gender)) + ggtitle("Gender") + xlab("Gender") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p2 <- ggplot(bank.churn, aes(x=Geography)) + ggtitle("Geography") + xlab("Geography") + 
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p3 <- ggplot(bank.churn, aes(x=HasCrCard)) + ggtitle("Has Credit Card") + xlab("Has Credit Card") + 
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p4 <- ggplot(bank.churn, aes(x=IsActiveMember)) + ggtitle("Is Active Member") + xlab("Is Active Member") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p5 <- ggplot(bank.churn, aes(x=Exited)) + ggtitle("Has Closed Account") + xlab("Has Closed Account") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
p6 <- ggplot(bank.churn, aes(x=tenure_group)) + ggtitle("Tenure Group") + xlab("Tenure Group") +
  geom_bar(aes(y = 100*(..count..)/sum(..count..)), width = 0.5) + ylab("Percentage") + coord_flip() + theme_dark() + geom_bar(fill = "lightblue")
grid.arrange(p1, p2, p3, p4, p5, p6, ncol=3)
```



## Balance the dataset before modeling
#### Load Library 
```{r}
library(ggplot2)
library(knitr)
suppressMessages(library(dplyr))
suppressMessages(library(unbalanced))
```

#### Intial look at the data 
##### Converted exited to factor
```{r}
bank.churn$Class<-as.factor(bank.churn$Exited) 
levels(bank.churn$Exited) <- c('Loyal', 'Closed') 
summary(bank.churn$Exited)
```
##### Plotting number of samples in each class
```{r}
options(scipen=10000) 

ggplot(data = bank.churn, aes(fill = Exited)) +
    geom_bar(aes(x = Exited))+
    ggtitle("Has customer closed the bank account or a loyal customer", subtitle = "Original dataset")+
    xlab("")+
    ylab("Samples")+
    scale_y_continuous(expand = c(0,0))+
    scale_x_discrete(expand = c(0,0))+
    theme(legend.position = "none", 
         legend.title = element_blank(),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank())
```

#### Seperating the data into the predictor variable and the response variable 
```{r}
predictor_variables <- bank.churn[,-13] 
response_variable <- bank.churn$Exited 
```

#### Minority case must have the facotr level of 1, default has it coded as 0
```{r}
levels(train) <- c('0', '1')
```

#### Run undersampled function 
```{r}
undersampled_data <- ubBalance(predictor_variables, 
                               response_variable, 
                               type='ubUnder',         
                               verbose = TRUE)
```
```{r}
undersampled_combined <- cbind(undersampled_data$X,    
                               undersampled_data$Y)

names(undersampled_combined)[names(undersampled_combined) == "undersampled_data$Y"] <- "Exited" 
levels(undersampled_combined$Exited) <- c('Loyal', 'Closed')
```

#### Plot number of cases in undersampled dataset
```{r}
ggplot(data = undersampled_combined, aes(fill = Exited))+
    geom_bar(aes(x = Exited))+
    ggtitle("Number customer who closed the bank account or remained a loyal customer after undersampling", 
            subtitle="Total samples: 4074")+
     xlab("")+
     ylab("Samples")+
     scale_y_continuous(expand = c(0,0))+
     scale_x_discrete(expand = c(0,0))+
     theme(legend.position = "none", 
           legend.title = element_blank(),
           panel.grid.major = element_blank(),
           panel.grid.minor = element_blank(),
           panel.background = element_blank())
```


#### Set your random seed to 1 and create a training and test split using the sample.split() function in the caTools library, with 70% of the observations in the training set and 30% in the testing set
```{r}
set.seed(1)
library(caTools)
split = sample.split(bank.churn$Exited, SplitRatio = 0.7)
train = subset(bank.churn, split ==TRUE)
test = subset(bank.churn, split == FALSE)
```
#### sample.split() balances the dependent variable between the training and testing sets
#### What is the (test) accuracy of this baseline model?
```{r}
z = table(test$Exited)
z[1]/sum(z)
```
#### Accuracy = .7963333
#### What is the (test) true positive rate of this baseline model?
```{r}
z = table (test$Exited)
z[2]/sum(z)
```
#### True Positive Rate = .796333
#### What is the (test) false positive rate of this baseline model?
```{r}
z = table (test$Exited)
z[1]/sum(z)
```
#### False Positive Rate = .203667



## Log Transformation 
```{r}
library(e1071)
```

```{r}
ggplot(data = bank.churn, aes(Age)) +
geom_histogram()
```

```{r}
skewness(bank.churn$Age)
```

```{r}
log_age <- log10(bank.churn$Age)
```

```{r}
ggplot(data = bank.churn, aes(log_age)) +
geom_histogram()
```

## Evaluation (three different models)
```{r}
log.model1 <- lm(log_age~Tenure, data = bank.churn)
log.model2 <-lm(log_age~Tenure + Gender, data = bank.churn)
log.model3 <- lm(log_age~Tenure + Gender + Balance, data = bank.churn)
```

```{r}
anova(log.model1 ,log.model2)
```

```{r}
anova(log.model2,log.model3)
```

```{r}
anova(log.model1, log.model3)
```




